Autonomous Realization of Simple Machines

### 2014-05-26 doc/paper/paper.tex
Got the initial draft of the pictures with arrows. Next: Remove text
finished the typical run figure. next: weight shift figure
results ve discussion kaldi

\documentclass[runningheads,a4paper]{llncs}
% \documentclass{article}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\usepackage[algoruled, vlined,linesnumbered]{algorithm2e}

@@

The manipulation of multiple objects under motor and perception uncertainty requires a series of 
robust strategies both algorithmicly and in practical implementation. In this work, a wide range of
motion planning tools are adopted such as rapidly-expanding random trees (RRTs) \cite{kuffner2000rrt},
analytical inverse kinematics \cite{tolani2000real} and Jacobian control \cite{whitney1969resolved}. 
Additionally, to handle perception errors, we propose using guarded moves \cite{bejczy1977effect} 
that control the manipulator behavior until a predetermined tactile feedback is received. Moreover,
we deploy ``conformant motion'' behaviors where the robot action forces itself
and its environment to a desired state without any sensory feedback \cite{goldman1996expressive}.

\subsubsection{Motion planning}

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/asdf.png}
  \caption{The mechanical advantage in forces}
  \label{fig:showOff}
\end{figure}

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/asdfg.png}
  \caption{The mechanical advantage in forces}
  \label{fig:showOff}
\end{figure}

% The robot has to move its arms out of the way to visualize the objects.

>>>>

\documentclass[runningheads,a4paper]{llncs}
% \documentclass{article}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\usepackage[algoruled, vlined,linesnumbered]{algorithm2e}
\usepackage{color}

@@

The manipulation of multiple objects under motor and perception uncertainty requires a series of 
robust strategies both algorithmicly and in practical implementation. In this work, a wide range of
motion planning tools are adopted such as rapidly-expanding random trees (RRTs) \cite{kuffner2000rrt},
analytical inverse kinematics \cite{tolani2000real} and Jacobian control \cite{whitney1969resolved}. 
Additionally, to handle perception errors, we propose using guarded moves \cite{bejczy1977effect} 
that control the manipulator behavior until a predetermined tactile feedback is received. Moreover,
we deploy ``conformant motion'' behaviors where the robot action forces itself
and its environment to a desired state without any sensory feedback \cite{goldman1996expressive}. 
% 
\subsubsection{Motion planning}

@@

Golem Krang is tasked with overturning a 45 kg load using a lever-fulcrum assembly with a limit of
\textcolor{red}{TBA} Nm on the force it can apply to the environment. Given the dimensions of the 
available objects in the environment, the robot has to design a structure, locate the components,
configure them into their positions and actuate the simple machine. In the following section, we
describe a typical run, focusing on details of perception, locomotion and manipulation.

Placed in a random configuration in the room, Golem Krang begins by scanning the room for the 
available objects and find the closest cinder block that would be used as a fulcrum (see Figure \ref{fig:typical_a}).
The scanning process is composed of a set of atomic behaviors which allow the robot to raise
its torso while sitting on the ground and move its arms out of its sight to avoid occlusions.
Once the fulcrum is located, the robot starts balancing and approaching the robot, until it 
positions itself in a predetermined distance to grasp the object. Using the motion planning tools,
such as RRTs and guarded moves, the robot grasps the cinder block at its top.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/a.png}
  \caption{Once Golem Krang detects the closest cinder block (left), it approaches (middle) and grasps
  the objects (right). Scene continues in Figure \ref{fig:typical_b}.}
  \label{fig:typical_a}
\end{figure}

An interesting observation we expand on in Section 4 is about how the location of a manipulated object
and the uneven distribution of its weight over the wheels affect the locomotion accuracy. To minimize
such an artifact, in Figure \ref{fig:typical_b}, Golem Krang first moves the grasped cinder block 
to the middle of its torso before turning around and localizing the load object at 45 kg. Having
detected the load, the final configuration of the fulcrum is deduced from the assembly design and
the robot places it appropriately.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/b.png}
  \caption{Having grasped the fulcrum, the robot localizes the load and places the fulcrum
		in the initial design configuration. Scene continues in Figure \ref{fig:typical_c}.} 
	\label{fig:typical_b}
\end{figure}

In the third part of the experiment, Golem Krang needs to detect and localize a candidate lever
object and grasp it, as shown in Figure \ref{fig:typical_c}. Given the size of the lever and the
noisy perception data, we propose using the wheels to localize the lever object more accurately
once the robot approaches it. Figure \ref{fig:typical_c}b displays the conformant behavior where the 
robot moves forward slowly to collide with the lever and have its localization error fixed. The
left wheel first makes contact and the contact overcomes the input torque, while the right wheel 
keeps moving until the robot is parallel and directly in front of the lever.

\begin{figure}[ht!]  	
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/c.png}
  \caption{The lever is picked up by first using vision and then running
	the wheels against the object to make physical contact before manipulation. Scene continues 
	in Figure \ref{fig:typical_d}.}
  \label{fig:typical_c}
\end{figure}

To simplify the locomotion, we have assumed collision-free paths and when Golem Krang carries the
lever, we ensure that the lever is carried high enough that it does not collide with other objects
(see Figure \ref{fig:typical_d}. Once the robot repositions itself in front of the robot, using
guarded moves, the robot first pushes the lever against the load horizontal to ensure it is at
the correct horizontal distance and then raises it until the design specification. Once at the
correct height, the robot releases the lever and allows it to slide on the fulcrum into the load
 - one of the more practically challenging tasks. For addition tasks, we have used task-constraint
 manipulation with online perception to minimize the errors during this routine. Finally, in
 Figure \ref{fig:typical_d}c, the robot pushes the object at the desired contact point and overturns
it.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/d.png}
  \caption{The mechanical advantage in forces}
  \label{fig:typical_d}
\end{figure}

\section{Results}

In this section, we provide experimental results on the functionality of the realized simple
machines under different conditions, study the sources of inaccuracies in the assembly process
and provide some insights on the autonomous manipulation of heavy objects.

\subsection{Designs with Different Load Weights and Lever Choices}
